\begin{enumerate}

\item \textbf{Burocracy issues}:\\
One of the most dangerous risks is related to the interaction with local government. The acquiring of permissions could take a long time, depending on the city, and this could lead in a major delay in our project. To prevent this we overestimate the time needed to obtain those permissions.
\item \textbf{Data loss}:\\
Data loss can be a consequence to hackers' attack or power supply issues. To avoid this problem we need to backup our data frequently on multiple external disks.
\item \textbf{Stakeholders' bankrupt}:\\
Since we have been commissioned this project by a private company and all the costs are covered by them, a bankrupt of that company would mean an almost certain failure for our software company. To prevent this, we ask them a financial guarantee.
\item \textbf{Dependency on external services}:\\
As we exploit external services in our project, like GoogleMaps, Payment services and Notification services, we might encounter compatibility problems if any of the external provider introduces major changes in the way services are provided.
A kind of preventive solution could involve exploiting information hiding and designing components in a modular way, in order to isolate the interface with those external services and make it easier to replace.
\item \textbf{Changes in requirememnts}:\\
Following a meeting with the stakeholders, some controversy concerning our interpretation of the requirements might arise. To avoid to make major changes to our project, we will schedule many meetings with the stakeholder in order to minimize incomprehensions by keeping a constant flow of information between our software house and the company.
\item \textbf{Low appeal to user}:\\
Once the software is released, we will incurr in user's review of our pruduct. To address better their taste, we will release beta versions of the client side during the development process, in order to collect opinions and adjust our work prior to actual releas. This will prevent us from applyng big changes right after the actual release, and will help us to develop a better product.
\end{enumerate}