\subsection{Revision History}
\subsection{Purpose and Scope}
The purpose of this document is to present the Project Plan for PowerEnJoy platform. We will first estimate the size of the project in all its parts. Upon this estimation, we will estimate the cost of the project exploiting COCOMO II estimation parameters and equations.\\
After that we will schedule tasks and allocate resource to them. To present this we are using Gantt diagrams.\\
Finally we're going to analyze possible risks we migth face during development, providing preventive solutions.
\subsection{Definitions, Acronyms, Abbreviations}
\subsubsection{Definitions}
\subsubsection{Acronyms}
\begin{itemize}
	\item FP: Function Points.
	\item ILF: Internal logic file
	\item ELF: External logic file.
	\item EI: External Input.
	\item EO: External Output.
	\item EQ: External Inquiries.
	\item UI: User Interface.
	\item GPS: Global Positioning System.
\end{itemize}
\subsubsection{Abbreviations}
\subsection{Reference Documents}
\begin{itemize}
	\item \href{https://github.com/StefanoBoriero/PowerEnjoy_Boriero_Brunitti/blob/master/Assignments%20AA%202016-2017.pdf}{Assignment}
\item \href{https://github.com/StefanoBoriero/PowerEnjoy_Boriero_Brunitti/blob/master/releases/RASD_v1.md}{RASD}
\item \href{https://github.com/StefanoBoriero/PowerEnjoy_Boriero_Brunitti/blob/master/releases/DD_v1.1.pdf}{Desing Document}
	\item \href{https://github.com/StefanoBoriero/PowerEnjoy_Boriero_Brunitti/blob/master/releases/ITPD_v1.pdf} Integration Testing Project Document
	\item \href{http://sunset.usc.edu/research/COCOMOII/expert_cocomo/drivers.html}{COCOMO II Cost Drivers}
	\item \href{http://csse.usc.edu/csse/research/COCOMOII/cocomo2000.0/CII_modelman2000.0.pdf}{COCOMO II Documentation}
\end{itemize} 